XXX

### 2012-03-25 paper/engNERwiki.tex
Got rid of some XXXs.

Wikipedia is a free, multilingual Internet encyclopedia, written collaboratively by volunteers\footnote{http://en.wikipedia.org/wiki/Wikipedia}. It is a goldmine of information; at the time of writing, Wikipedia contains about 21 million interlinked articles. Of these, 3,903,467 are English and 212,120 are Hungarian. XXX %kell ez ide?

@@

Wikipedia's knowledge may be incorporated as features in NER learning, e.g.~Kazama and Torisawa \shortcite{Kazama:07} showed that automatic extraction of category labels from Wikipedia improves the accuracy of a supervised NE-tagger.

@@

Thanks for the huge amount of Wikipedia articles, the possibility of building large enough 
%(XXX ez mit jelent?) elég nagy :)
corpora is given for less resourced languages, as well. Since our method is mainly XXX language-independent, it can be easily applied for languages which are structurally differing from English. Hungarian is a highly agglutinative language, with free word order and other particularities XXX detailed later in section \ref{sec:hun}. There are human annotated CoNLL-style datasets, but the one presented here is the first automatically NE-annotated corpus for Hungarian.

@@

Our goal is to create a large NE-annotated corpus, automatically generated from Wikipedia articles. We follow a similar path XXX to \cite{Nothman:08}, who broke up XXX the process into four steps:

@@

In this section, we describe how these steps were implemented. While the approach in essence is language-independent, the exact details XXX have to be accomodated to the target language. This section explains the general idea and its execution for English; the next section describes how the idea is adapted to Hungarian.

@@

From the available NER annotation standards we elected to use the CoNLL \cite{Tjong:03} NE types. It is not difficult to see the parallels XXX between the DBpedia sub-hierarchies \texttt{Person}, \texttt{Organisation} and \texttt{Place} and the CoNLL NE categories PERSON, ORGANIZATION and LOCATION. The fourth category, MISCELLANEOUS is more elusive; according to the ConLL NER annotation guide\footnote{http://www.cnts.ua.ac.be/conll2003/ner/annotation.txt}, the sub-hierarchies \texttt{Event} and \texttt{Work} belong to this category, as well as various other classes outside the main hierarchies.

@@

The first approach, unfortunately, already fails to assign the correct ConLL NE tag to our only example. The reason behind this failure is that multiple parents in an ontology show an inherent ambiguity in the class in question: it is entirely natural to think of a library as a location as well as a public organization. DBpedia's guidelines prefers Organisation, while ConLL's one refers it as a Location. Therefore, only the second, manual approach ensures correct tagging. XXX

>>>>

Wikipedia is a free, multilingual Internet encyclopedia, written collaboratively by volunteers\footnote{http://en.wikipedia.org/wiki/Wikipedia}. It is a goldmine of information; at the time of writing, Wikipedia contains about 21 million interlinked articles. Of these, 3,903,467 are English and 212,120 are Hungarian.

@@

The knowledge in Wikipedia may be incorporated as features in NER learning, e.g.~Kazama and Torisawa \shortcite{Kazama:07} showed that automatic extraction of category labels from Wikipedia improves the accuracy of a supervised NE-tagger.

@@

Thanks for the huge amount of Wikipedia articles, the possibility of building large enough 
%(XXX ez mit jelent?) elég nagy :)
corpora is given for less resourced languages, as well. Since our method is mainly XXX language-independent, it can be easily applied for languages which are structurally differing from English. Hungarian is a highly agglutinative language, with free word order and other particularities detailed later in section \ref{sec:hun}. There are human annotated CoNLL-style datasets, but the one presented here is the first automatically NE-annotated corpus for Hungarian.

@@

Our goal is to create a large NE-annotated corpus, automatically generated from Wikipedia articles. We follow a similar path to \cite{Nothman:08}, who broke down the process into four steps:

@@

In this section, we describe how these steps were implemented. While the approach in essence is language-independent, the exact details have to be accomodated to the target language. This section explains the general idea and its execution for English; the next section describes how the idea is adapted to Hungarian.

@@

From the available NER annotation standards we elected to use the CoNLL \cite{Tjong:03} NE types. It is not difficult to see the parallels between the DBpedia sub-hierarchies \texttt{Person}, \texttt{Organisation} and \texttt{Place} and the CoNLL NE categories PERSON, ORGANIZATION and LOCATION. The fourth category, MISCELLANEOUS is more elusive; according to the ConLL NER annotation guide\footnote{http://www.cnts.ua.ac.be/conll2003/ner/annotation.txt}, the sub-hierarchies \texttt{Event} and \texttt{Work} belong to this category, as well as various other classes outside the main hierarchies.

@@

The first approach, unfortunately, already fails to assign the correct ConLL NE tag to our only example. The reason behind this failure is that multiple parents in an ontology show an inherent ambiguity in the class in question: it is entirely natural to think of a library as a location as well as a public organization. DBpedia's guidelines prefers Organisation, while ConLL's one refers it as a Location. Therefore, only the second, manual approach ensures correct tagging.
